---
output: html_document
---

We'll use the following functions throughout this lesson:

```{r, echo=FALSE}
int_to_string <- function(x){
  c("one", "two", "three", "four", "five",
    "six", "seven", "eight", "nine", "ten")[x]
}

gt <- function(a, b){
  a > b
}

is_even <- function(x){
  x %% 2 == 0
}

square <- function(x){
  x^2
}

add_talk <- function(x, y){
  message("x is ", x)
  message("y is ", y, "\n")
  x + y
}

paste_talk <- function(x, y){
  message("x is ", x)
  message("y is ", y, "\n")
  paste0(x, y)
}
```

## `int_to_string(x)`

Covert a number into its string equivaluent.

```{r}
int_to_string(4)
```

## `gt(a, b)`

Returns `TRUE` if `a` is greater than `b`, otherwise returns `FALSE`.

```{r}
gt(3, 1)
gt(2, 5)
```

## `is_even(x)`

Returns `TRUE` is `x` is even, otherwise returns `FALSE`.

```{r}
is_even(34)
is_even(55)
```

## `square(x)`

Computes the square of `x`.

```{r}
square(4)
```

## `add_talk(x, y)`

Adds `x` and `y` and produces a message about which numbers are being added.

```{r}
add_talk(5, 3)
```

## `paste_talk(x, y)`

Concatenates the strings `x` and `y` and produces a message about which stirngs
are being concatenated.

```{r}
paste_talk("red", "head")
```